Verifying Demonstrations

### 2018-05-31 paper/DB-anon-cred.tex
Adds WIP table of security for DB Schnorr
Addresses Seb's comment on describing Anon-Pass

\emph{Reattempting a distance-bounding Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition of also not being secure against terrorist fraud either.
We now propose another way to turn the Schnorr protocol into a public-key \iac{DB} protocol which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating verifier.

>>>>

\emph{Reattempting a distance-bounding Schnorr protocol.}%
\label{DBSchnorr}
In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition of also not being secure against terrorist fraud either.
We now propose another way to turn the Schnorr protocol into a public-key \iac{DB} protocol which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating verifier.
